### 2025-02-02 src/paper/paper.tex
temp

The data from SchizConnect was filtered based on MRI field strength and clinical diagnosis. We retrieved only images captured with 3T MRI scans. This was done to ensure uniformity of the data obtained.

>>>>

The data from SchizConnect was filtered based on MRI field strength and clinical diagnosis. We retrieved only images captured with 3T MRI scans. This was done to ensure uniformity of the data obtained. Figure~\ref{fig:raw_mri_volume_slices} presents the example of raw data.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{./figs/sample_volume.png} % test_pipeline.png
    \caption{Three image slices representing the average of a 3D column in three views: dorsal, lateral, and superior respectively}\label{fig:raw_mri_volume_slices}
\end{figure}
